Figures main manuscript

### 2020-03-30 code/05_figures-and-correlations.rmd
Made Fig 3 correlations APA compliant

Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 67 effects. Tau is not directly comparable across effect size measures.

@@

Figure 2. Simulated $I^2$  densities across 68 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 68 meta-analyses. Each simulated density consists of approximately 680,000 estimates.

@@

labels <- tau_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>% #fitter is a sourced function
  mutate(lab = paste0("r = ", r, " ", fig3_ci$ci)) #put output into one variable for improved plotting

@@

```{r corr_per_effect_type-plot, cache = FALSE}
#tau plot----
tau_facet <- ggplot(tau_per_type, aes(x = eff_size, y = tau)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", tau))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

Figure 3. The Pearson correlation between absolute effect size and A) $\hat{\tau}$, B) $I^2$ and C) $H^2$ respectively for 40 effects that were measured as mean or standardized mean differences and 10 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects. Effects reported as mean differences were standardized and odds ratios/risk differences computed as log odds ratios. Square brackets contain 95% bootstrapped percentile confidence intervals. Code to reproduce figure: osf.io/zuwpg/?view_only=e6639d8d4f924739a7310782fbbb4e06

>>>>

*Figure 1.* Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 67 effects. Tau ($\tau$) is not directly comparable across effect size measures. Code to reproduce table: osf.io/u2t3r

@@

*Figure 2.* Simulated $I^2$  densities across 68 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 68 meta-analyses. Each simulated density consists of approximately 680,000 estimates. *MD* = Mean Difference, *SMD* = Standardized Mean Difference. Code to reproduce table: osf.io/u2t3r

@@

labels <- tau_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>% #fitter is a sourced function
  mutate(lab = paste0("r (", c(rep(8, 3), rep(41, 3)), ") = ",
                      gsub("0\\.", "\\.", r),
                      ", 95% CI ",
                      gsub("0\\.", "\\.", fig3_ci$ci))) #put output into one variable for improved plotting

@@

```{r corr_per_effect_type-plot, cache = FALSE}
#tau plot----
tau_facet <- ggplot(tau_per_type, aes(x = eff_size, y = tau)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.06, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", tau))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.06, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.06, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Absolute Effect Size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

@@

*Figure 3.* The Pearson correlation between absolute effect size and A) $\hat{\tau}$, B) $I^2$ and C) $H^2$ respectively for 43 effects that were measured as mean or standardized mean differences and 10 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects. Effects reported as mean differences were standardized and odds ratios/risk differences computed as log odds ratios. *r* = Product-moment correlation, square brackets contain 95% bootstrapped percentile confidence intervals. Code to reproduce figure: osf.io/u2t3r
